\documentclass[10pt,a4paper]{article}

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% lmodern not required — using default CM fonts
\usepackage[margin=1.8cm, top=1.6cm, bottom=1.6cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}
% microtype requires scalable fonts; omit if using bitmap fonts

%% Colors
\definecolor{accent}{RGB}{0, 90, 160}
\definecolor{lightgray}{RGB}{130, 130, 130}

%% Hyperlinks
\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent,
}

%% Section formatting
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}
  [\vspace{-4pt}\rule{\linewidth}{0.8pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{10pt}{6pt}

%% List formatting
\setlist[itemize]{leftmargin=1.4em, topsep=2pt, itemsep=1pt, parsep=0pt}

%% Custom commands
\newcommand{\cvevent}[4]{%
  \noindent\textbf{#1}\hfill{\small\color{lightgray}#3}\\
  \textit{#2}\hfill{\small\color{lightgray}#4}
  \vspace{2pt}
}

\pagestyle{empty}

\begin{document}

\begin{center}
  {\Huge\bfseries Kevin Galim}\\[2pt]
  {\normalsize\color{lightgray} Senior AI Research Engineer | Efficient LLM Inference, Post-Training, AI Systems}\\[2pt]
  \small
  galimkevin@gmail.com $\cdot$
  \href{https://kevingalim.com}{kevingalim.com} $\cdot$
  \href{https://scholar.google.com/citations?user=G1EpeWYAAAAJ}{scholar.google.com} $\cdot$
  \href{https://www.linkedin.com/in/kgalim/}{linkedin.com/in/kgalim/}
\end{center}
\vspace{4pt}

\section{Summary}
Machine learning researcher working on efficient LLM inference, post-training systems, and accelerator-aware generative model pipelines. First/co-first author of publications at ICLR, ICML, ACL, ECCV, and WACV, with work spanning KV-cache and prompt/context compression, diffusion LLM parallel decoding, and parameter-efficient adaptation for state space models.


\section{Experience}
\cvevent{Senior AI Research Engineer}{FuriosaAI}{Jun 2021 -- Present}{Seoul, South Korea}
\begin{itemize}
  \item Conducted research on large-scale generative models and LLMs, including efficient inference (KV-cache optimization, diffusion LLMs), scalable training (PEFT, state space models), and advanced architectures.
  \item Studied post-training systems including asynchronous OPD/RL-style pipelines, stale rollout effects, teacher-cache constraints, and throughput--quality trade-offs.
  \item Co-authored multiple first- and co-first-author papers in top-tier conferences: ICLR, ICML, ACL, CVPR, ECCV, and WACV.
  \item Designed end-to-end pipelines for training and evaluating LLMs, including accelerator-aware rollout generation and inference pipelines on custom AI hardware.
\end{itemize}
\vspace{6pt}

\cvevent{AI/Computer vision research and development}{Funzin}{Mar 2020 -- Jun 2021}{Seoul, South Korea}
\begin{itemize}
  \item Developed computer-vision models for object detection, segmentation, gesture detection, and autonomous golf cart perception.
  \item Optimized models for embedded deployment using TensorRT, OpenVINO, Coral, DSP acceleration, and ARM NEON.
  \item Built and demonstrated a real-time OpenGL 3D surround-view system at CES 2021.
\end{itemize}
\noindent\textit{\small Technologies: PyTorch, TensorFlow, C++, Python, TensorRT, OpenVINO, ARM NEON}
\vspace{6pt}

\cvevent{Web / AR Developer}{Freelance}{Aug 2019 -- Mar 2020}{Munich}
\begin{itemize}
  \item Built AR mobile apps, cloud-backed web apps, and cross-platform mobile apps using Unity3D, Flutter, AWS, and Google Cloud.
\end{itemize}
\noindent\textit{\small Technologies: Unity3D, C\#, JavaScript, Flutter, AWS, Google Cloud}
\vspace{6pt}

\cvevent{C++/CUDA software engineer}{ARRI}{Aug 2015 -- Sep 2016}{Munich}
\begin{itemize}
  \item Developed GPU-accelerated image-processing algorithms using CUDA and OpenCL.
  \item Built C++/OpenGL visualization and image-analysis tools for digital cinema workflows.
\end{itemize}
\noindent\textit{\small Technologies: C++, CUDA, OpenGL, OpenCL}
\vspace{6pt}


\section{Ongoing Work}
\begin{itemize}[leftmargin=1.2em]
  \item \textbf{AsyncOPD: How Stale Can On-Policy Distillation Be?}.
\textit{Submitted manuscript}, 2026.\\
Studies stale rollouts, KL-direction sensitivity, teacher-cache constraints, estimator design, and throughput--quality trade-offs in asynchronous on-policy distillation pipelines.
\end{itemize}

\section{Publications {\normalfont\small (* denotes equal contribution)}}

\subsection*{First-author / co-first-author publications}

\begin{itemize}[leftmargin=1.2em]
  \item \textbf{Kevin Galim}*, Ethan Ewer*, Wonjun Kang, Minjae Lee, Hyung Il Koo, Kangwook Lee.
Draft-based Approximate Inference for LLMs.
\textit{ICLR}, 2026.
  \item Wonjun Kang*, \textbf{Kevin Galim}*, Seunghyuk Oh*, Minjae Lee, Yuchen Zeng, Shuibai Zhang, Coleman Hooper, Yuezhou Hu, Hyung Il Koo, Nam Ik Cho, et al.
ParallelBench: Understanding the Trade-offs of Parallel Decoding in Diffusion LLMs.
\textit{ICLR}, 2026.
  \item Wonjun Kang*, \textbf{Kevin Galim}*, Yuchen Zeng*, Minjae Lee, Hyung Il Koo, Nam Ik Cho.
State-offset Tuning: State-based Parameter-Efficient Fine-Tuning for State Space Models.
\textit{ACL}, 2025.
  \item \textbf{Kevin Galim}*, Wonjun Kang*, Yuchen Zeng*, Hyung Il Koo, Kangwook Lee.
Parameter-Efficient Fine-Tuning of State Space Models.
\textit{ICML}, 2025.
  \item Wonjun Kang*, \textbf{Kevin Galim}*, Hyung Il Koo, Nam Ik Cho.
Counting Guidance for High Fidelity Text-to-Image Synthesis.
\textit{WACV (Oral)}, 2025.
  \item Wonjun Kang*, \textbf{Kevin Galim}*, Hyung Il Koo.
Eta Inversion: Designing an Optimal Eta Function for Diffusion-based Real Image Editing.
\textit{ECCV}, 2024.
\end{itemize}

\subsection*{Other publications}

\begin{itemize}[leftmargin=1.2em]
  \item Seunghyuk Oh, Minjae Lee, \textbf{Kevin Galim}, Minseo Kim, Hyung Koo, Wonjun Kang, Hanbaek Lyu, Kangwook Lee.
Inference-Aligned SFT for Diffusion LLMs via Group-based Trajectory Sampling.
\textit{ICLR DeLTa Workshop}, 2026.
  \item Minjae Lee*, Wonjun Kang*, Byeongkeun Ahn, Christian Classen, \textbf{Kevin Galim}, Seunghyuk Oh, Minghao Yan, Hyung Il Koo, Kangwook Lee.
TABED: Test-Time Adaptive Ensemble Drafting for Robust Speculative Decoding in LVLMs.
\textit{EACL}, 2026.
  \item Wonjun Kang, Byeongkeun Ahn, Minjae Lee, \textbf{Kevin Galim}, Seunghyuk Oh, Hyung Il Koo, Nam Ik Cho.
UNCAGE: Contrastive Attention Guidance for Masked Generative Transformers in Text-to-Image Generation.
\textit{IEEE Access}, 2026.
  \item Maxim Maximov, \textbf{Kevin Galim}, Laura Leal-Taixe.
Focus on Defocus: Bridging the Synthetic to Real Domain Gap for Depth Estimation.
\textit{CVPR}, 2020.
\end{itemize}


\section{Education}
\cvevent{Technical University of Munich}{Master's degree, Informatics: Games Engineering}{2016 -- 2019}{}
\noindent{\small\color{lightgray}Grade: 1.4 (German system)}
\vspace{6pt}

\cvevent{The University of Tokyo}{Research, Computer Graphics}{2017 -- 2018}{}
\vspace{6pt}

\cvevent{Technical University of Munich}{Bachelor's degree, Informatics: Games Engineering}{2013 -- 2016}{}
\noindent{\small\color{lightgray}Grade: 1.6 (German system)}
\vspace{6pt}


\section{Skills}

\noindent
\textbf{LLM Inference \& Post-Training:} Speculative Decoding $\cdot$ KV-Cache Optimization $\cdot$ Prompt/Context Compression $\cdot$ On-Policy Distillation $\cdot$ Efficient Inference \\[2pt]
\textbf{Machine Learning Research:} Large Language Models $\cdot$ Diffusion Models $\cdot$ Parameter-Efficient Fine-Tuning $\cdot$ State Space Models $\cdot$ Diffusion LLMs \\[2pt]
\textbf{Computer Vision:} Object Detection $\cdot$ Image Segmentation $\cdot$ Depth Estimation $\cdot$ Generative Models \\[2pt]
\textbf{Programming:} Python $\cdot$ C++ $\cdot$ CUDA $\cdot$ PyTorch $\cdot$ TensorFlow $\cdot$ JavaScript
\section{Languages}
\noindent English (Full professional proficiency) $\cdot$ German (Native or bilingual proficiency) $\cdot$ Korean (Professional working proficiency)

\end{document}